[dcpo_demsupport]

### 2020-08-04 paper/dcpo_demsupport.Rmd
add {plm} to dependencies

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

```{r dcpo-uncertainty}
# Preload function ----
vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  plm,
  tidyverse # data wrangling
)

@@

```{r dcpo-uncertainty}
# Preload function ----
vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}
